\vspace{1.0cm} \Large \bf Supplemental material of ``Health and disease imprinted in the time variability of the human microbiome''

### 2016-09-25 mSystems/mSys_MAIN.tex
Minor changes to mSys_MAIN to adapt to mSystems' staff requirements
On branch master
	modified:   mSys_MAIN.pdf
	modified:   mSys_MAIN.tex
	modified:   mSys_suppl.pdf
	modified:   mSys_suppl.tex

%%% PACKAGES
\usepackage{lmodern} % Activa fuentes y macros de Latin Modern
\usepackage[T1]{fontenc} % set font encoding
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage[english]{babel} 
\usepackage[expert, charter]{mathdesign} % Fuentes... disponibles conjuntos {charter|utopia}
%%\usepackage{calligra}
\usepackage[printwatermark]{xwatermark}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{parskip}
%%\usepackage{float}
\usepackage[nolists,tablesfirst, nomarkers]{endfloat}
\usepackage{moreverb} % for verbatim output

@@

% watermarks (time consuming!)
\newwatermark[allpages,color=Purple!4,angle=45,scale=7,xpos=-40,ypos=0]{submitted}
\newwatermark[allpages,color=Purple!12,angle=0,scale=1,xpos=0,ypos=137]{
\emph{mSystems} \LaTeX\ manuscript \releasecode\ submission}

@@

% bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,font=small]{caption}

@@

%% M&M
% Selection and Methods
\bibitem{Einstein} {\bf Einstein A.} 1905. Über die von der molekularkinetischen Theorie der Wärme geforderte Bewegung von in ruhenden Flüssigkeiten suspendierten Teilchen. Annalen der Physik, {\bf 322}:549-560.
\bibitem{QIIME} {\bf Caporaso JG, Kuczynski J, Stombaugh J, Bittinger K, Bushman FD, Costello EK, Fierer N, Peña AG, Goodrich JK, Gordon JI, Huttley G a, Kelley ST, Knights D, Koenig JE, Ley RE, Lozupone C a, Mcdonald D, Muegge BD, Pirrung M, Reeder J, Sevinsky JR, Turnbaugh PJ, Walters W a, Widmann J, Yatsunenko T, Zaneveld J, Knight R.} 2010. correspondence QIIME allows analysis of high- throughput community sequencing data Intensity normalization improves color calling in SOLiD sequencing. Nat Publ Gr {\bf 7}:335–336.
\bibitem{LMAT} {\bf Ames SK, Hysom DA, Gardner SN, Lloyd GS, Gokhale MB, Allen JE}.  2013. Scalable metagenomic taxonomy classification using a reference genome database.  Bioinformatics {\bf 29}:2253-2260.
\bibitem{FASTX} {\bf Gordon, A, Hannon, GJ.} 2010. FASTX-Toolkit. FASTQ/A shortreads pre-processing tools v0.0.13. http://hannonlab.cshl.edu/fastx\_toolkit/ (last accessed 26 Jul 2016).
\bibitem{SILVA} {\bf Quast C, Pruesse E, Yilmaz P, Gerken J, Schweer T, Yarza P, Peplies J, Glöckner FO}. 2013. The SILVA ribosomal RNA gene database project: improved data processing and web-based tools. Acids Res. {\bf 41}:D590-D596
\bibitem{LMAT2} {\bf Ames SK, Gardner SN, Marti JM, Slezak TR, Gokhale MB, Allen JE}. 2015. Using populations of human and microbial genomes for organism detection in metagenomes. Genome Res. {\bf 25}:1056-67.
\bibitem{boot} {\bf Wu, C.F.J.} 1986. Jackknife, bootstrap and other resampling methods in regression analysis. (with discussions) \textit{The Annals of Statistics} {\bf 14}:1261-1350 
\bibitem{biopwrlaw} {\bf Xiao X, White EP, Hooten MB, Durham SL}. 2011. On the use of log-transformation vs. nonlinear regression for analyzing biological power laws. Ecology {\bf 92}:1887-1894
\end{thebibliography}
\end{document}

>>>>

%%% PACKAGES
\usepackage{lmodern} % Activa fuentes y macros de Latin Modern
\usepackage[T1]{fontenc} % set font encoding
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage[english]{babel} 
\usepackage[expert, charter]{mathdesign} % Fuentes... disponibles conjuntos {charter|utopia}
%%\usepackage{calligra}
\usepackage[printwatermark]{xwatermark}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{parskip}
%%\usepackage{float}
\usepackage[nolists, nomarkers]{endfloat}
\usepackage{moreverb} % for verbatim output

@@

% watermarks (time consuming!)
%\newwatermark[allpages,color=Purple!4,angle=45,scale=7,xpos=-40,ypos=0]{submitted}
%\newwatermark[allpages,color=Purple!12,angle=0,scale=1,xpos=0,ypos=137]{
%\emph{mSystems} \LaTeX\ manuscript \releasecode\ submission}

@@

% bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,font=small]{caption}
\captionsetup[table]{name=Supplementary Table S\!\!} % See EOF

@@

%% M&M
% Selection and Methods
\bibitem{Einstein} {\bf Einstein A.} 1905. Über die von der molekularkinetischen Theorie der Wärme geforderte Bewegung von in ruhenden Flüssigkeiten suspendierten Teilchen. Annalen der Physik, {\bf 322}:549-560.
\bibitem{QIIME} {\bf Caporaso JG, Kuczynski J, Stombaugh J, Bittinger K, Bushman FD, Costello EK, Fierer N, Peña AG, Goodrich JK, Gordon JI, Huttley G a, Kelley ST, Knights D, Koenig JE, Ley RE, Lozupone C a, Mcdonald D, Muegge BD, Pirrung M, Reeder J, Sevinsky JR, Turnbaugh PJ, Walters W a, Widmann J, Yatsunenko T, Zaneveld J, Knight R.} 2010. correspondence QIIME allows analysis of high- throughput community sequencing data Intensity normalization improves color calling in SOLiD sequencing. Nat Publ Gr {\bf 7}:335–336.
\bibitem{LMAT} {\bf Ames SK, Hysom DA, Gardner SN, Lloyd GS, Gokhale MB, Allen JE}.  2013. Scalable metagenomic taxonomy classification using a reference genome database.  Bioinformatics {\bf 29}:2253-2260.
\bibitem{FASTX} {\bf Gordon, A, Hannon, GJ.} 2010. FASTX-Toolkit. FASTQ/A shortreads pre-processing tools v0.0.13. http://hannonlab.cshl.edu/fastx\_toolkit/ (last accessed 26 Jul 2016).
\bibitem{SILVA} {\bf Quast C, Pruesse E, Yilmaz P, Gerken J, Schweer T, Yarza P, Peplies J, Glöckner FO}. 2013. The SILVA ribosomal RNA gene database project: improved data processing and web-based tools. Acids Res. {\bf 41}:D590-D596
\bibitem{LMAT2} {\bf Ames SK, Gardner SN, Marti JM, Slezak TR, Gokhale MB, Allen JE}. 2015. Using populations of human and microbial genomes for organism detection in metagenomes. Genome Res. {\bf 25}:1056-67.
\bibitem{boot} {\bf Wu, C.F.J.} 1986. Jackknife, bootstrap and other resampling methods in regression analysis. (with discussions) \textit{The Annals of Statistics} {\bf 14}:1261-1350 
\bibitem{biopwrlaw} {\bf Xiao X, White EP, Hooten MB, Durham SL}. 2011. On the use of log-transformation vs. nonlinear regression for analyzing biological power laws. Ecology {\bf 92}:1887-1894
\end{thebibliography}

%% mSystems staff asked to send the captions of the supplementary tables at the end
%%  of the main text PDF.
\begin{table}
  \caption{Taylor parameters. Individuals with either animal-based (A) or plant-based (P) diets\cite{diet}. Previous to diet,  the population sampled is described by $\bar{V} = 0.09 \pm 0.05, \bar{\beta} = 0.77 \pm 0.04$.}

\caption{Taylor parameters for individuals taking antibiotics\cite{antibiotic}. Prior to antibiotics intake, the population sampled is described by $\bar{V} = 0.12 \pm 0.05, \bar{\beta} = 0.75 \pm 0.04$.}

\caption{Taylor parameters for persons diagnosed with irritable bowel syndrome (IBS)\cite{IBS}. Healthy individuals sampled in this study are characterized by $\bar{V} = 0.134 \pm 0.009, \bar{\beta} = 0.691 \pm 0.025$.}

\caption{Taylor parameters for the healthy subject of the discordant twins\cite{kwashiorkor}. This table continues in Supplementary Table S\ref{tab:DK}. The population of healthy twins is characterized by $\bar{V} = 0.25 \pm 0.10, \bar{\beta} = 0.863 \pm 0.028$.}\label{tab:DH}

\caption{Taylor parameters for the kwashiorkor part of the discordant twins\cite{kwashiorkor}. This is a continuation of Supplementary Table S\ref{tab:DH}. The population of healthy twins is characterized by $\bar{V} = 0.25 \pm 0.10, \bar{\beta} = 0.863 \pm 0.028$.}\label{tab:DK}

\caption{Taylor parameters for individuals with different degrees of overweight and obesity\cite{LEA}. Healthy people in this study, whom were not obese, are characterized by $\bar{V} = 0.19 \pm 0.06, \bar{\beta} = 0.806 \pm 0.034$.} 
\end{table}

\end{document}
